Windowed least-squares model reduction for dynamical systems

### 2019-10-16 section4/spatial_numerical.tex
workin on section 4.2.1

&\residLMSArg{n,i} (\stateFOMDiscreteArg{n,i},\ldots,\stateFOMDiscreteArg{n,i-\lmsWidthArg{n}{i}}) = \bz, \qquad i=1,\ldots,\nstepsArg{n}, \\

@@

\residArg{n,i} &: (\stateyDiscreteArgnt{i},\ldots,\stateyDiscreteArgnt{i-\lmsWidthArg{n}{i}}) \mapsto  \frac{1}{\Delta t^{n,i}} \sum_{j=0}^{\lmsWidthArg{n}{i}} \alpha^{n,i}_j \stateyDiscreteArgnt{i-j} -  \sum_{j=0}^{\lmsWidthArg{n}{i}} \beta^{n,i}_j \velocity(\stateyDiscreteArgnt{i-j},\timeWindowArg{n}{i-j}) \\

@@

denotes the time step, $\lmsWidthArg{n}{i}$ denotes the number of time steps employed by the scheme at the $i$th time instance over the $n$th window, and

@@

define the specific type of multistep scheme. 
\begin{remark}\label{remark:LMS}
For notational simplicity, we assume the linear multistep method employs time
	instances from only within the current time window. In general, the linear
	multistep method at the $n$th window could be designed to employ multiple
	time instances from previous time windows. \KTC{What are the implications of
	this? I suggest removing this and adding a simple condition, maybe with a
	footnote.}
\end{remark}

@@

Employing a linear multistep method allows the objective \textit{functional}~\eqref{eq:obj} to be replaced with the objective \textit{function}

@@

\objectiveArgLMS{n} &\vcentcolon (\stateyDiscreteArgnt{0},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto
\frac{1}{2} \sum_{i=1}^{\nstepsArg{n}} \quadWeightsLMSScalarArg{n}{i} [\residArg{n,i}(\stateyDiscreteArgnt{i},\ldots, \stateyDiscreteArgnt{i-\lmsWidthArg{n}{i})})]^T  \stweightingMatArgt{n}{\timeWindowArg{n}{i}} \residArg{n,i}(\stateyDiscreteArgnt{i},\ldots, \stateyDiscreteArgnt{i-\lmsWidthArg{n}{i}}), \\
&\vcentcolon \RR{\fomdim} \otimes \RR{\nstepsArg{n}+1} \rightarrow

@@

%where 
%\residArg{n,i} &: (\stateyArgnt{n,i},\ldots,\stateyArgnt{n,i-k(i)}) \mapsto  \sum_{j=0}^k \alpha_j \stateyArgnt{n,i-j} = \Delta t^{n,i} \sum_{j=0}^k \beta_j \velocity(\stateyArgnt{n,i-j}),
%               &: \RR{\fomdim} \otimes \RR{k(i)} \rightarrow \RR{\fomdim}, 
%is the discrete residual resulting from the linear multistep scheme and 
where $\quadWeightsLMSScalarArg{n}{i} \in \RR{}$ are quadrature weights.
\KTC{Don't these weights need to be non-negative to guarantee the integral is
non-negative? If so, then specify $\quadWeightsLMSScalarArg{n}{i} \in\RR{}_+$}
\methodAcronym\ sequentially computes the solutions
$\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$,
	\KTC{What is $\genstate^{n-1}(\timeEndArg{n-1} ) $ doing here? Two problems
	(1) there is no notion of a generalized coordinate $\genstate$ yet, and (2)
	this should be the discrete solution, not the exact solution evaluated at
	the final time.}
	&\underset{(\stateyDiscreteArgnt{0},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \in \trialspace\otimes \RR{\lmsWidthArg{n}{i}+1}}{\text{minimize } }
\objectiveArgLMS{n} (\stateyDiscreteArgnt{0},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \\
& \text{subject to} \hspace{0.2 in}  \stateyDiscreteArg{0} =
\begin{cases} \basisspaceArg{n} \spatialIC + \stateInterceptArg{n}& n = 2,\ldots,\nslabs,\\
\basisspaceArg{1} \genstateICOne  + \stateInterceptArg{1}& n=1. \end{cases} \end{align*}
%\methodAcronym\ solves the minimization problem over each time window, 
%&\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}} = \underset{\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}} \in \trialspace}{\text{arg\,min } }
%\objectiveArgLMS{n} (\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}}) \\
%& \text{subject to} \hspace{0.2 in}  \approxstateDiscreteArg{n,0} =
%\begin{cases} \approxstateDiscreteArg{n-1,\nstepsArg{n-1}} & n = 2,\ldots,\nslabs,\\
%\approxstateIC & n=1. \end{cases} \end{align*}
	Equivalently, WLS sequentially computes the generalized
	coordinates
	$\genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\timeWindowArg{n}{i}}$,
	$n=1,\ldots,\nslabs$ 
with $\genstateDiscreteArg{n,i}(\approx
	\genstateArgnt{n}(\timeWindowArg{n}{i}))\in\RR{\romdim}$
	that satisfy
\begin{equation}\label{eq:obj_gen_lms_final}
	&
	\underset{(\genstateyDiscreteArg{0},\ldots,\genstateyDiscreteArg{\nstepsArg{n}})\in\RR{\romdim}\otimes \RR{\lmsWidthArg{n}{i}+1}}{\text{minimize } }
\objectiveArgLMS{n} (\basisspaceArg{n} \genstateyDiscreteArg{0} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateyDiscreteArg{\nstepsArg{n}} + \stateInterceptArg{n}) \\ 
& \text{subject to} \hspace{0.2 in}
\genstateyDiscreteArg{0} =
\begin{cases} \spatialIC & n = 2,\ldots,\nslabs \\
\genstateICOne& n=1. \end{cases} 

@@

%\begin{equation}\label{eq:obj_gen_lms_final}
%\begin{split}
%& \genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}}  = \underset{\genstateyDiscreteArg{n,0},\ldots,\genstateyDiscreteArg{n,\nstepsArg{n}}}{\text{arg\,min } }
%\objectiveArgLMS{n} (\basisspace \genstateyDiscreteArg{n,0} + \stateIntercept,\ldots,\basisspace \genstateyDiscreteArg{n,\nstepsArg{n}} + \stateIntercept) \\ 
%& \text{subject to} \hspace{0.2 in}
%\genstateDiscreteArg{n,0} =
%\begin{cases} \genstateDiscreteArg{n-1, \nstepsArg{n-1}} & n = 2,\ldots,\nslabs \\
%\basisspace^T(\stateFOMIC - \stateIntercept)& n=1. \end{cases} 
%\end{split}
The optimization problem takes the form of a \textit{weighted least-squares
	problem}. \KTC{I got rid of (non)linear. If it's either linear or nonlinear,
	then omit it as an adjective, as this is no longer descriptive. }
We emphasize that optimization problem~\eqref{eq:obj_gen_lms_final} associates
	with an \spatialAcronym\ trial subspace characterized by a reduction in
	spatial complexity, but no reduction in temporal complexity.

@@

\begin{remark}
For the limiting case where $\nstepsArg{n} = 1$ such that the window size is equivalent to the time step, $\DeltaSlabArg{n} \equiv \timeWindowArg{n}{1} - \timeWindowArg{n}{0}$, and uniform 
quadrature weights are used, \methodAcronym\ with \spatialAcronym\ trial
	subspaces solved via the direct approach recovers LSPG. \KTC{Not exactly. To
	make this LSPG as presented earlier, also require the time grid here to
	align with the time grid used for time integration earlier. Also, this
	formulation requires allowing the stencil to go back to time steps at
	previous windows.} 
\end{remark} 
\subsubsection{Solution to the least-squares problem through the Gauss--Newton method}
	\KTC{If the dynamics are linear, doesn't this just yield a linear
	least-squares problem that can be solved directly? We need to present this
	more clearly.}
Discretization through linear multistep methods (as well as other techniques) 
results in a (non)linear least-squares problem.
A variety of algorithms exist for solving least-squares problems, including trust region approaches, the Gauss–Newton method, and the Levenberg–Marquardt method.  
The numerical experiments presented in this work consider the Gauss--Newton method, and as such we outline this approach here.

To describe the Gauss--Newton method, we first define a ``vectorization" function 
\begin{align*}
 \unroll &\vcentcolon (\stateyDiscreteArg{1},\ldots,\stateyDiscreteArg{m} ) \mapsto \begin{bmatrix} [\stateyDiscreteArg{1}]^T & \ldots & [\stateyDiscreteArg{m}]^T \end{bmatrix}^T  \\
&\vcentcolon \RR{p} \otimes \RR{m} \rightarrow \RR{pm}.
\end{align*}
The vectorized generalized coordinates over the $n$th time window are then
defined as \KTC{notationally, why are we doing a double bar instead of a bar?}
\begin{equation*}
\genstatecollocMatSlabArg{n} \defeq 
\unroll (\genstateDiscreteArg{n,1},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}} ).
\end{equation*}
We now define the weighted space--time residual over the entire window as
\KTC{To make this valid for seeping back into the previous time window, the
second argument could be omitted here (okay because there is already a
superscript on the residual) and arbitrary previous solutions could be
included in the first residual here.}
\begin{equation*}
\residLMSSlabArg{n} : (\genstatecollocMatySlabArg{};\genstateDiscreteArg{n,0}) \mapsto \begin{bmatrix}
 \sqrt{\quadWeightsLMSScalarArg{n}{1} } \stweightingMatOneArg{n} \residLMSArg{n,1}( \basisspaceArg{n} \genstateyDiscreteArgnt{1} + \stateInterceptArg{n},  \basisspaceArg{n} \genstateDiscreteArg{n,0} + \stateInterceptArg{n},) \\
\vdots \\
 \sqrt{\quadWeightsLMSScalarArg{n}{\nstepsArg{n}} } \stweightingMatOneArg{n} \residLMSArg{n,\nstepsArg{n}}( \basisspaceArg{n} \genstateyDiscreteArgnt{\nstepsArg{n}} + \stateInterceptArg{n}, \ldots,\basisspaceArg{n} \genstateyDiscreteArgnt{\nstepsArg{n} - k^n(\nstepsArg{n}) } + \stateInterceptArg{n}) \\
\end{bmatrix},
\end{equation*}
where $\genstatecollocMatySlabArg{} \defeq \unroll (\genstateyDiscreteArg{1},\ldots,\genstateyDiscreteArg{\nstepsArg{n}} ).$
It is worth noting that, by design, \KTC{This is incorrect. Missing a 1/2
factor}
\begin{equation*}
\objectiveArgLMS{n} \bigg( \basisspaceArg{n} \genstateDiscreteArg{n,0} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateDiscreteArg{n,\nstepsArg{n}} + \stateInterceptArg{n} \ \bigg) 
=
\bigg[\residLMSSlabArg{n}  (\genstatecollocMatSlabArg{n};\genstateDiscreteArg{n,0}) \bigg]^T \bigg[ \residLMSSlabArg{n}(\genstatecollocMatSlabArg{n};\genstateDiscreteArg{n,0}) \bigg].
\end{equation*} 
Using these definitions, Algorithm~\ref{alg:colloc_gn} presents the standard Gauss--Newton method. The algorithm consists of three fundamental steps: (1) compute the FOM O$\Delta$E residual given the current guess, (2) compute the Jacobian of the residual over the time window and form the normal equations, and (3) solve the normal equations and update the state.

>>>>

&\residLMSArg{n,i} (\stateFOMDiscreteArg{n,i};\stateFOMDiscreteArg{n,i-1},\ldots,\stateFOMDiscreteArg{n,i-\lmsWidthArg{n}{i}}) = \bz, \qquad i=1,\ldots,\nstepsArg{n}, \\

@@

\residArg{n,i} &: (\stateyDiscreteArgnt{i};\stateyDiscreteArgnt{i-1},\ldots,\stateyDiscreteArgnt{i-\lmsWidthArg{n}{i}}) \mapsto  \frac{1}{\Delta t^{n,i}} \sum_{j=0}^{\lmsWidthArg{n}{i}} \alpha^{n,i}_j \stateyDiscreteArgnt{i-j} -  \sum_{j=0}^{\lmsWidthArg{n}{i}} \beta^{n,i}_j \velocity(\stateyDiscreteArgnt{i-j},\timeWindowArg{n}{i-j}) \\

@@

denotes the time step, $\lmsWidthArg{n}{i}$ denotes the number of time steps employed by the scheme at the $i$th time instance over the $n$th window and

@@

define the specific type of multistep scheme. To handle the case where the linear multistep method employs time instances from the previous window(s), we enforce the condition on the indices $(n,i) = (n-1,\nstepsArg{n-1}+i)$ for $i<0$. 
%\begin{remark}\label{remark:LMS}
%For notational simplicity, we assume the linear multistep method employs time
%	instances from only within the current time window. In general, the linear
%	multistep method at the $n$th window could be designed to employ multiple
%	time instances from previous time windows. \KTC{What are the implications of
%	this? I suggest removing this and adding a simple condition, maybe with a
%	footnote.}
%\end{remark}

@@

\EP{In the process of reworking this slightly, need to take care for the case where we are employing multiple time steps 
from the previous window. Still cleaning up}
\methodAcronym\ with the direct approach and a linear multistep method sequentially computes the solutions
$\approxstateDiscreteArg{n,1},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$,
%	\KTC{What is $\genstate^{n-1}(\timeEndArg{n-1} ) $ doing here? Two problems
%	(1) there is no notion of a generalized coordinate $\genstate$ yet, and (2)
%	this should be the discrete solution, not the exact solution evaluated at
%	the final time.} \EP{You are correct, I think there is an error now in the minimize term though. It was $\in \trialspace\otimes \RR{\lmsWidthArg{n}{i}+1}$, it should be $\trialspace\otimes \RR{\nstepsArg{n}+1}$}
	&\underset{(\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \in \trialspace\otimes \RR{\nstepsArg{n}{i}}}{\text{minimize } }
\objectiveArgLMS{n} (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}). 
%%& \text{subject to} \hspace{0.2 in}  \stateyDiscreteArg{0} =
%%\begin{cases} \basisspaceArg{n} \spatialICDiscrete + \stateInterceptArg{n}& n = 2,\ldots,\nslabs,\\
%\basisspaceArg{1} \genstateICOne  + \stateInterceptArg{1}& n=1. \end{cases} 
%Employing a linear multistep method allows the objective \textit{functional}~\eqref{eq:obj} to be replaced with the objective \textit{function}
%\EP{Had to change the definition of the objective function to reflect stepping back into previous window}
In the above, $\objectiveArgLMS{n}$ is the discrete objective function at the $n$th time window and is defined as

@@

\objectiveArgLMS{n} &\vcentcolon (\stateyDiscreteArgnt{1},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \mapsto
\frac{1}{2} \sum_{i=1}^{\nstepsArg{n}} \quadWeightsLMSScalarArg{n}{i} [\residArg{n,i}(\stateyDiscreteArgnt{i};\ldots, \stateyDiscreteArgnt{i-\lmsWidthArg{n}{i})})]^T  \stweightingMatArgt{n}{\timeWindowArg{n}{i}} \residArg{n,i}(\stateyDiscreteArgnt{i};\ldots, \stateyDiscreteArgnt{i-\lmsWidthArg{n}{i}}), \\
&\vcentcolon \RR{\fomdim} \otimes \RR{\nstepsArg{n}} \rightarrow

@@

where $\quadWeightsLMSScalarArg{n}{i} \in \RRplus$ are quadrature weights and, for $i \le 0$ in $\objectiveArgLMS{n}$, we take
\begin{equation}\label{eq:wls_spatial_direct_args}
\stateyDiscreteArgnt{i}  \equiv 
\begin{cases}
\basisspaceArg{n} \basisspaceTArg{n} (\approxstateDiscreteArg{n-1,\nstepsArg{n-1}+i} - \stateInterceptArg{n}) + \stateInterceptArg{n} & n = 2,\ldots,\nslabs,  \\
\basisspaceArg{n} \basisspaceTArg{n} (\stateFOMIC - \stateInterceptArg{n}) + \stateInterceptArg{n} & n = 1.
\end{cases}

@@

Note that the boundary conditions are automatically satisfied by Eq.~\eqref{eq:wls_spatial_direct_args}.

%where 
%\begin{align*}
%\residArg{n,i} &: (\stateyArgnt{n,i},\ldots,\stateyArgnt{n,i-k(i)}) \mapsto  \sum_{j=0}^k \alpha_j \stateyArgnt{n,i-j} = \Delta t^{n,i} \sum_{j=0}^k \beta_j \velocity(\stateyArgnt{n,i-j}),
%\\
%               &: \RR{\fomdim} \otimes \RR{k(i)} \rightarrow \RR{\fomdim}, 
%\end{align*} 
%is the discrete residual resulting from the linear multistep scheme and 
%\methodAcronym\ solves the minimization problem over each time window, 
%\begin{align*}
%&\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}} = \underset{\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}} \in \trialspace}{\text{arg\,min } }
%\objectiveArgLMS{n} (\stateyDiscreteArgnt{n,0},\ldots,\stateyDiscreteArgnt{n,\nstepsArg{n}}) \\
%& \text{subject to} \hspace{0.2 in}  \approxstateDiscreteArg{n,0} =
%\begin{cases} \approxstateDiscreteArg{n-1,\nstepsArg{n-1}} & n = 2,\ldots,\nslabs,\\
%\approxstateIC & n=1. \end{cases} \end{align*}
	Equivalently, \methodAcronym\ sequentially computes the generalized
	coordinates
	$\genstateDiscreteArg{n,1},\ldots,\genstateDiscreteArg{n,\timeWindowArg{n}{i}}$,
	$n=1,\ldots,\nslabs$ 
with $\genstateDiscreteArg{n,i}(\approx
	\genstateArgnt{n}(\timeWindowArg{n}{i}))\in\RR{\romdim}$
	that satisfy
\begin{equation}\label{eq:obj_gen_lms_final}
\begin{split}
	&
	\underset{(\genstateyDiscreteArg{1},\ldots,\genstateyDiscreteArg{\nstepsArg{n}})\in\RR{\romdim}\otimes \RR{\nstepsArg{n}}}{\text{minimize } }
\objectiveArgLMS{n} (\basisspaceArg{n} \genstateyDiscreteArg{1} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateyDiscreteArg{\nstepsArg{n}} + \stateInterceptArg{n}). 
%& \text{subject to} \hspace{0.2 in}
%\genstateyDiscreteArg{0} =
%\begin{cases} \genspatialICDiscrete  & n = 2,\ldots,\nslabs \\
%\genstateICOne& n=1. \end{cases} 
\end{split}
\end{equation}
%\begin{equation}\label{eq:obj_gen_lms_final}
%\begin{split}
%& \genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}}  = \underset{\genstateyDiscreteArg{n,0},\ldots,\genstateyDiscreteArg{n,\nstepsArg{n}}}{\text{arg\,min } }
%\objectiveArgLMS{n} (\basisspace \genstateyDiscreteArg{n,0} + \stateIntercept,\ldots,\basisspace \genstateyDiscreteArg{n,\nstepsArg{n}} + \stateIntercept) \\ 
%& \text{subject to} \hspace{0.2 in}
%\genstateDiscreteArg{n,0} =
%\begin{cases} \genstateDiscreteArg{n-1, \nstepsArg{n-1}} & n = 2,\ldots,\nslabs \\
%\basisspace^T(\stateFOMIC - \stateIntercept)& n=1. \end{cases} 
%\end{split}
%\end{equation}
The optimization problem takes the form of a \textit{weighted least-squares
	problem}. \KTC{I got rid of (non)linear. If it's either linear or nonlinear,
	then omit it as an adjective, as this is no longer descriptive. }
We emphasize that optimization problem~\eqref{eq:obj_gen_lms_final} associates
	with an \spatialAcronym\ trial subspace characterized by a reduction in
	spatial complexity, but no reduction in temporal complexity.

@@

\begin{remark}
For the limiting case where $\nstepsArg{n} = 1$ such that the window size is equivalent to the time step, $\DeltaSlabArg{n} \equiv \timeWindowArg{n}{1} - \timeWindowArg{n}{0}$, uniform 
quadrature weights are used, and uniform bases and weighting matrices are used, 
\methodAcronym\ with \spatialAcronym\ trial
	subspaces solved via the direct approach recovers LSPG. \KTC{Not exactly. To
	make this LSPG as presented earlier, also require the time grid here to
	align with the time grid used for time integration earlier. Also, this
	formulation requires allowing the stencil to go back to time steps at
	previous windows.} \EP{I agree with the second comment, to be 100\% precise we need to go back into other time windows. Clearly you can do this if you would like, and I think the comment clarifies this. Hopefully can avoid this now with the condition you mentioned. I think the first comment is not required. The LSPG ``approach" minimizes the residual at a time instance; it isn't tied to the description we gave earlier.} 
\end{remark} 
\subsubsection{Solution to the least-squares problem through the Gauss--Newton method}
	\KTC{If the dynamics are linear, doesn't this just yield a linear
	least-squares problem that can be solved directly? We need to present this
	more clearly.}
Discretization through linear multistep methods (as well as other techniques) 
results in a (non)linear least-squares problem.
A variety of algorithms exist for solving least-squares problems, including trust region approaches, the Gauss–Newton method, and the Levenberg–Marquardt method.  
The numerical experiments presented in this work consider the Gauss--Newton method, and as such we outline this approach here.

To describe the Gauss--Newton method, we first define a ``vectorization" function 
\begin{align*}
 \unroll &\vcentcolon (\stateyDiscreteArg{1},\ldots,\stateyDiscreteArg{m} ) \mapsto \begin{bmatrix} [\stateyDiscreteArg{1}]^T & \ldots & [\stateyDiscreteArg{m}]^T \end{bmatrix}^T  \\
&\vcentcolon \RR{p} \otimes \RR{m} \rightarrow \RR{pm}.
\end{align*}
The vectorized generalized coordinates over the $n$th time window are then
defined as \KTC{notationally, why are we doing a double bar instead of a bar?}
\EP{The notation for space--time in 2.4 uses bars. I don't want to confuse these generalized coordinates with those, they conceptually two different things} 
\begin{equation*}
\genstatecollocMatSlabArg{n} \defeq 
\unroll (\genstateDiscreteArg{n,1},\ldots,\genstateDiscreteArg{n,\nstepsArg{n}} ).
\end{equation*}
We now define the weighted space--time residual over the entire window as
\KTC{To make this valid for seeping back into the previous time window, the
second argument could be omitted here (okay because there is already a
superscript on the residual) and arbitrary previous solutions could be
included in the first residual here.}
\begin{equation*}
\residLMSSlabArg{n} : (\genstatecollocMatySlabArg{};\genstateDiscreteArg{n,0}) \mapsto \begin{bmatrix}
 \sqrt{\quadWeightsLMSScalarArg{n}{1} } \stweightingMatOneArg{n} \residLMSArg{n,1}( \basisspaceArg{n} \genstateyDiscreteArgnt{1} + \stateInterceptArg{n},  \basisspaceArg{n} \genstateDiscreteArg{n,0} + \stateInterceptArg{n},) \\
\vdots \\
 \sqrt{\quadWeightsLMSScalarArg{n}{\nstepsArg{n}} } \stweightingMatOneArg{n} \residLMSArg{n,\nstepsArg{n}}( \basisspaceArg{n} \genstateyDiscreteArgnt{\nstepsArg{n}} + \stateInterceptArg{n}, \ldots,\basisspaceArg{n} \genstateyDiscreteArgnt{\nstepsArg{n} - k^n(\nstepsArg{n}) } + \stateInterceptArg{n}) \\
\end{bmatrix},
\end{equation*}
where $\genstatecollocMatySlabArg{} \defeq \unroll (\genstateyDiscreteArg{1},\ldots,\genstateyDiscreteArg{\nstepsArg{n}} ).$
It is worth noting that, by design, \KTC{This is incorrect. Missing a 1/2
factor}
\begin{equation*}
\objectiveArgLMS{n} \bigg( \basisspaceArg{n} \genstateDiscreteArg{n,0} + \stateInterceptArg{n},\ldots,\basisspaceArg{n} \genstateDiscreteArg{n,\nstepsArg{n}} + \stateInterceptArg{n} \ \bigg) 
=
\bigg[\residLMSSlabArg{n}  (\genstatecollocMatSlabArg{n};\genstateDiscreteArg{n,0}) \bigg]^T \bigg[ \residLMSSlabArg{n}(\genstatecollocMatSlabArg{n};\genstateDiscreteArg{n,0}) \bigg].
\end{equation*} 
Using these definitions, Algorithm~\ref{alg:colloc_gn} presents the standard Gauss--Newton method. The algorithm consists of three fundamental steps: (1) compute the FOM O$\Delta$E residual given the current guess, (2) compute the Jacobian of the residual over the time window and form the normal equations, and (3) solve the normal equations and update the state.
